---
title: "Untitled"
author: "Church Army's Research Unit"
date: "Some-date"
output:
  word_document:
    reference_docx: caRefDoc.docx
---

```{r behindTheScenes, include = FALSE, echo = FALSE}
#Five hashes is a fifth level heading, which is set to be a pagebreak in the reference document
#NB I think this template needs a little work
knitr::opts_chunk$set(echo = FALSE)

leaders <- readRDS("O:\\WCC\\Learning and Development\\Research\\PROJECT - Portsmouth 2019 onwards\\Data\\leaders & attenders\\leadersResponses2018and2019.rdat")

attenders <- readRDS("O:\\WCC\\Learning and Development\\Research\\PROJECT - Portsmouth 2019 onwards\\Data\\leaders & attenders\\attenders2018NoUnderFives.rdat")

# ^ Note that the above files are coming from 'static' locations - there are no markdown files that will automatically update any of that stuff. 
```

```{r libraries, include = FALSE}
library("mapsapi")
library("dplyr")
library("magrittr")
library("stringr")
library("purrr")
library("XML")
library("sf")
library("ggmap")
library("ggplot2")
library("ggmap")
```

```{r createArchitecture}
suppressWarnings(dir.create(here::here("data")))
```

```{r getGoogleCoords}
### Looking to get Google Coordinates
### 
### if(the coordinates exist){just use them}
### otherwise{try to make them by looking for a google maps api key}
### but if(you can't find an api key){throw a very informative error}

### Look for GMaps API Key --------------------------------------------------------------
  lookForKeyHere <- "O:\\WCC\\Learning and Development\\Research\\Team member folders\\Dave Lovell\\keys\\googleMapsApi.csv"

  if(file.exists(here::here("data\\googleMapsApi.csv"))) {
    
    #Look for key in data
    googleKey <- read.csv(here::here("data\\googleMapsApi.csv"))
    message("Maps API key found in \\data")
    
  } else if(file.exists(lookForKeyHere)) {
    
    # Look for key in O: drive, save to data if found
    googleKey <- read.csv(lookForKeyHere)
    write.csv(googleKey, here::here("data\\googleMapsApi.csv"))
    message("Maps API key found on O drive. Saving to \\data")
      
  } else {
    # Throw error if key cannot be found
    stop("'googleMapsApi.csv' not found in \\data or on O Drive.
Either establish connection to 'O:\\\\', or talk to Dave Lovell
to get the csv, or get your own key and write a .csv with fields
`client` and `key`")
  }

### Separate key and client data -------------------------------------------------
  googleClient <- googleKey$client
  googleKey <- googleKey$key

### Look for lat/long data -------------------------------------------------------    
if(file.exists(here::here("data\\latLong.rdat")))
{
  latLongTib <- readRDS(here::here("data\\latLong.rdat"))
  leaders %<>% 
    left_join(latLongTib, by = "responseId")
  
  message("latLong.rdat found in \\data")
  
} else {
    
  message("googleCoords.rdat not located in \\data.
Using Google Maps API key to generate coordinates")

  # Cut websites from info_venueDetails to get addresses
  leaders %<>%
    mutate(address =
             info_venueDetails %>% 
             # This took a while - regex often counterintuitive
             # remove a string that has spaces (or eols) on either side
             # and otherwise consists of any number of anything but spaces
             # on either side of a '.co' or '.com' or '.org' or '.uk'
    str_remove_all("(?<=[:space:]|^)[^[:space:]]*(\\.co|\\.com|\\.org|\\.uk)[^[:space:]]*(?=[:space:]|$)"))
  
  ### coordGet function - use API to get xml w/ coords, then extract coords from XML ----------------
  coordGet <-
  function(address, key) {
    
    if(!is.character(address)|is.na(address)) {
      
      lat = NA
      lng = NA } else {
        
        mapsapi::mp_geocode(addresses = address, key = key)[[1]] %>% #shouldn't be longer than 1
      (XML::xmlParse) ->
      someXML
    
      XML::getNodeSet(someXML,"/GeocodeResponse/result/geometry/location/lat") ->
        latNode
      XML::getNodeSet(someXML, "/GeocodeResponse/result/geometry/location/lng") ->
        lngNode
  
      latNode %>% 
        (XML::toString.XMLNode) %>%
        str_extract("(?<=(<lat>)).+(?=(</lat>))") %>% 
        as.numeric ->
        lat
      
      lngNode  %>% 
        (XML::toString.XMLNode) %>%
        str_extract("(?<=(<lng>)).+(?=(</lng>))") %>% 
        as.numeric ->
        lng
      }
    
          coords <- list("lat" = lat,"lng" = lng)
      
      return(coords)
    }

  ### Run coordGet on each address ---------------------------------
  leaders %<>%
    mutate(latLong = map(as.list(address),
                         ~ coordGet(address = ., key = googleKey)))
  ### create LatLongTib
  leaders %>% 
    select(responseId, address, latLong) ->
    latLongTib
  
  ### Save LatLongTib ----------------------------------------------
  latLongTib%>% 
    saveRDS(here::here("data\\latLong.rdat"))
  
  leaders %<>%
    left_join(latLongTib %>% 
                select(-address),
              by = "responseId")
  
} # Run the above if the google data doesn't exist
```
##### 

# Portsmouth Pioneer Project Evaluation Quantitative Report - Mock-up

## Pioneer Posts

At the beginning of the Pioneer Project, the ambition was to see 12 new fxC begun each with 50-100 worshippers and for 15% of the diocesan church attendance to be in fxC (from 1200 to 2200).

```{r makingAMap}

leaders %<>% 
  mutate(lat = map_dbl(latLong,
                       ~ unlist(.["lat"])),
         lng = map_dbl(latLong,
                       ~ unlist(.["lng"])))

mapLeaders <-
  leaders %>% 
  filter(!is.na(lat) & !is.na(lng)) %>% 
  st_as_sf(coords = c("lat", "lng"),
           # google Maps proj4:
           crs = "+proj=merc +a=6378137 +b=6378137 +lat_ts=0.0 +lon_0=0.0 +x_0=0.0 +y_0=0 +k=1.0 +units=m +nadgrids=@null +wktext  +no_defs",
           agr = "identity") # Because these are buildings.

# register_google(client = googleClient,
#                 key = googleKey)
# 
# basemap <- get_map(location = "Portsmouth, UK", zoom = 9, maptype = 'roadmap')
# 
# ggmap(basemap) +
#   geom_sf(data = mapLeaders,
#           colour = "black",
#           alpha = 0,
#           size = 1,
#           inherit.aes = FALSE)
# 
# ggplot(mapLeaders) +
#   geom_sf(aes(geometry = geometry))

```

* fxC data from leaders and attenders surveys
* list of initiatives that didn't meet fxC criteria
* look at all fxC but focus in on any links with pioneer posts
* any fxC started by 'voluntary lay pioneers'

## Harbour Church
The original project plan aimed to “plant a large, city centre, resourcing church appealing to younger people. Within the 5 year timescales, we expect this to have grown to at least 200 worshippers and to be exploring a further plant”. 

This ambition was achieved within 18 months of Harbour Church’s planting  

## Pioneer Training & Vocations

* 'How to pioneer' course - numbers attending
* Recognised lay pioneers
* Pioneers accepted for reader and ordination training
* Who do the diocese consider to be pioneers (beyond the 'official' ones)?

## Culture Change
