---
title: "Untitled"
author: "Church Army's Research Unit"
date: "Some-date"
output:
  word_document:
    reference_docx: caRefDoc.docx
---

```{r behindTheScenes, include = FALSE, echo = FALSE}
#Five hashes is a fifth level heading, which is set to be a pagebreak in the reference document
#NB I think this template needs a little work
knitr::opts_chunk$set(echo = FALSE)

leaders <- readRDS("O:\\WCC\\Learning and Development\\Research\\PROJECT - Portsmouth 2019 onwards\\Data\\leaders & attenders\\leadersResponses2018and2019.rdat")

attenders <- readRDS("O:\\WCC\\Learning and Development\\Research\\PROJECT - Portsmouth 2019 onwards\\Data\\leaders & attenders\\attenders2018NoUnderFives.rdat")

# ^ Note that the above files are coming from 'static' locations - there are no markdown files that will automatically update any of that stuff. 
```

```{r libraries}
library("RgoogleMaps")
library("dplyr")
library("magrittr")
```

##### 

```{r createArchitecture}
suppressWarnings(dir.create(here::here("data")))
```

```{r getGoogleCoords}
### Looking to get Google Coordinates
### 
### if(the coordinates exist){just use them}
### otherwise{try to make them by looking for a google maps api key}
### but if(you can't find an api key){throw a very informative error}
if(!file.exists(here::here("data/googleCoords.rdat")))
{
  googleCoords <- readRDS(here::here("data/googleCoords.rdat"))
  
  message("googleCoords.rdat found in \\data")
  
} else {
  
  lookForKeyHere <- "O:\\WCC\Learning and Development\\Research\\Team member folders\\Dave Lovell\\keys\\googleMapsApi.csv"
  message("googleCoords.rdat not located in \\data.
Searching for Google Maps API key to generate coordinates")
  
  if(file.exists(here::here("data\\googleMapsApi.csv"))) {
    
    googleKey <- read.csv(here::here("data\\googleMapsApi.csv"))
    message("Maps API key found in \\data")
    
  } else if(file.exists(file.exists(lookForKeyHere))) {
    
    googleKey <- read.csv(lookForKeyHere)
    write.csv(googleKey, here::here("data\\googleMapsApi.csv"))
    message("Maps API key found on O drive. Saving to \\data")
      
  } else stop("'googleCoords.rdat' not found in \\data
and googleMapsApi.csv not found in \\data or on O Drive.
Either establish connection to 'O:\\\\', or talk to Dave Lovell
to get the csv, or get your own key and write a .csv with fields
`client` and `key`")
}
```

# Portsmouth Pioneer Project Evaluation Quantitative Report - Mock-up

## Pioneer Posts

At the beginning of the Pioneer Project, the ambition was to see 12 new fxC begun each with 50-100 worshippers and for 15% of the diocesan church attendance to be in fxC (from 1200 to 2200).

* fxC data from leaders and attenders surveys
* list of initiatives that didn't meet fxC criteria
* look at all fxC but focus in on any links with pioneer posts
* any fxC started by 'voluntar lay pioneers'

## Harbour Church
The original project plan aimed to “plant a large, city centre, resourcing church appealing to younger people. Within the 5 year timescales, we expect this to have grown to at least 200 worshippers and to be exploring a further plant”. 

This ambition was achieved within 18 months of Harbour Church’s planting  

## Pioneer Training & Vocations

* 'How to pioneer' course - numbers attending
* Recognised lay pioneers
* Pioneers accepted for reader and ordination training
* Who do the diocese consider to be pioneers (beyond the 'official' ones)?

## Culture Change
