---
title: "Untitled"
author: "Church Army's Research Unit"
date: "Some-date"
output:
  word_document:
    reference_docx: caRefDoc.docx
---

```{r behindTheScenes, include = FALSE, echo = FALSE}
#Five hashes is a fifth level heading, which is set to be a pagebreak in the reference document
#NB I think this template needs a little work
knitr::opts_chunk$set(echo = FALSE)

leaders <- readRDS("O:\\WCC\\Learning and Development\\Research\\PROJECT - Portsmouth 2019 onwards\\Data\\leaders & attenders\\leadersResponses2018and2019.rdat")

attenders <- readRDS("O:\\WCC\\Learning and Development\\Research\\PROJECT - Portsmouth 2019 onwards\\Data\\leaders & attenders\\attenders2018NoUnderFives.rdat")

# ^ Note that the above files are coming from 'static' locations - there are no markdown files that will automatically update any of that stuff. 
```

```{r libraries}
library("RgoogleMaps")
library("dplyr")
library("magrittr")
```

##### 

```{r getGoogleCoords}
# leaders %>% 
here::here()
#   mutate(coord)
```

# Portsmouth Pioneer Project Evaluation Quantitative Report - Mock-up

## Pioneer Posts

At the beginning of the Pioneer Project, the ambition was to see 12 new fxC begun each with 50-100 worshippers and for 15% of the diocesan church attendance to be in fxC (from 1200 to 2200).

* fxC data from leaders and attenders surveys
* list of initiatives that didn't meet fxC criteria
* look at all fxC but focus in on any links with pioneer posts
* any fxC started by 'voluntar lay pioneers'

## Harbour Church
The original project plan aimed to “plant a large, city centre, resourcing church appealing to younger people. Within the 5 year timescales, we expect this to have grown to at least 200 worshippers and to be exploring a further plant”. 

This ambition was achieved within 18 months of Harbour Church’s planting  

## Pioneer Training & Vocations

* 'How to pioneer' course - numbers attending
* Recognised lay pioneers
* Pioneers accepted for reader and ordination training
* Who do the diocese consider to be pioneers (beyond the 'official' ones)?

## Culture Change
